POMDP comparisons across sigma_m, sigma_g

### 2017-10-06 appendix/appendix.Rmd
cannot fix id, overwrites outputs

```{r eval=FALSE}
log_dir <- "appendix_alphas" # Store the computed solution files here
dir.create(log_dir)
id = "pomdp_intro"    # an optional id for these runs

## POMDP solution (slow, >10,000 seconds per scenario, & memory intensive)
system.time(
  alphas <- 
    parallel::mclapply(1:length(models), 
    function(i){
      log_data <- data.frame(id = id, 
                             model = "gs", 
                             r = r, 
                             K = K, 
                             sigma_g = meta[i,"sigma_g"][[1]], 
                             sigma_m = meta[i,"sigma_m"][[1]], 
                             noise = "normal")

@@

```{r}
log_dir <- "../pomdp_intro"
meta <- meta_from_log("pomdp_intro", log_dir)
alphas <- alphas_from_log(meta, log_dir)
```

>>>>

```{r eval=TRUE}
log_dir <- "appendix_alphas" # Store the computed solution files here
dir.create(log_dir)

## POMDP solution (slow, >10,000 seconds per scenario, & memory intensive)
system.time(
  alphas <- 
    parallel::mclapply(1:length(models), 
    function(i){
      log_data <- data.frame(model = "gs", 
                             r = r, 
                             K = K, 
                             sigma_g = meta[i,"sigma_g"][[1]], 
                             sigma_m = meta[i,"sigma_m"][[1]], 
                             noise = "normal")

@@

```{r}
meta <- meta_from_log(data.frame(model="gs"), log_dir)
alphas <- alphas_from_log(meta, log_dir)
```
